%-------------------------------------
% Resum in LaTeX (XeLaTeX)
% Author:  HF Yuan
% Project: https://github.com/xyz-yuanhf/yuan-resume
% Base on: https://github.com/mattyHerzig/mattys_resume
%          http://www.jianxu.net/en/
% License: MIT
%------------------------------------

\documentclass[a4paper, 10pt]{article}
\usepackage{myresume}  % Style package
\usepackage{hyperref}

% --------------------  START  --------------------
\begin{document}

% -------------------- HEADING --------------------
\begin{flushright}
  \setstretch{0.6}
  % \item {\Calluna (+00) 111-2222-3333}  % Phone number
  \item {\Calluna \href{mailto:weilai@weilai.group}{weilai@weilai.group}}  % E-mail address
  \item {\Calluna \href{https://orcid.org/0009-0007-5002-0930}{https://orcid.org/0009-0007-5002-0930}}  % ORCID
  \item {\Calluna \href{https://github.com/WHULai}{https://github.com/WHULai}}  % Github
  \item {\Calluna \href{http://www.weilai.group}{http://www.weilai.group}}  % Home page
\end{flushright}\vspace{-45pt}

\begin{flushleft}  % Rplace here with your name (and identity if required)
  % {\Calluna \fontsize{30pt}{30pt}\selectfont \textsc{Xiao Yuan}} \quad {\Calluna \fontsize{14.5pt}{14.5pt}\selectfont \textsc{Ph.D.}}
  {\Calluna \fontsize{32pt}{32pt}\selectfont \textsc{Lai Wei}}
  \noindent\rule{\textwidth}{0.4pt}
\end{flushleft}

% -------------------- EDUCATION --------------------
\sectionBlock{
\section{Education}
}{
\iffalse
\eduHeading
  {Department of Automation, Tsinghua University}{Beijing, China}
  {Ph.D. in Control Science and Engineering}{2022 - 2028 \footnotesize{\textit{(expected)}}}
\itemListStart
  \myItem{Advisor: Prof. Xiao Yuan}
  \myItem{Research area: Operations Research and Machine Learning}
\itemListEnd
\fi

\eduHeading
  {Shool of Robotics, Wuhan University}{Hubei, China}
  {B.E. in Robotics Engineering}{2024 - 2028 \footnotesize{\textit{(expected)}}}
\itemListStart
  \myItem{GPA: 3.77/4.00.}
  \myItem{
    Selected Coursework:
    \begin{itemize}
      \item Linear Algebra (96)
      \item Theoretical Mechanics (92)
      \item University Physics (93)
    \end{itemize}
  }
\itemListEnd
}

\iffalse
% -------------------- PUBLICATIONS --------------------
\sectionBlock{
\section{Publications}
}{
\pubListStart
\justifying
\item \textbf{Xiao Yuan}, Hua Li. The Future Urban Transportation Systems: Innovations and Challenges. \textit{Journal of Operations Research and Optimization}, 2024.
\item Hua Li, \textbf{Xiao Yuan}, John Doe. Optimizing Logistics and Supply Chain Networks Using Machine Learning Techniques. \textit{International Conference on Operations Research and Machine Learning}, 2023.
\item John Doe, \textbf{Xiao Yuan}, Hua Li. Artificial Intelligence in Healthcare: Transforming Diagnostics and Treatment. \textit{International Conference on HealthTech Innovations}, 2023.
\pubListEnd
}
\fi

\iffalse
% -------------------- PROJECTS --------------------
\sectionBlock{
\section{Projects}
}{
\projHeading
{\textbf{Advanced Optimization Techniques for Smart Grid Management}}
{National Natural Science Foundation of China (NSFC)} {2023.01 - 2024.01}

\projHeading
{\textbf{Optimizing Urban Traffic Flow Using AI-Based Predictive Models}}
{Smart Transportation Innovations Grant} {2021.12 - 2022.12}.
}
\fi

\iffalse
% -------------------- INTERNSHIPS --------------------
\sectionBlock{
\section{Internships}
}{
\internHeading
  {ABC Tech Ltd.}{Shanghai, China}{2024.01 - 2024.06}
\itemListStart
  \myItem{Develop engaging content for social media platforms.}
  \myItem{Prepare reports and presentations summarizing research findings.}
\itemListEnd
\internHeading
  {XYZ Tech Inc.}{Shanghai, China}{2023.07 - 2023.12}
\itemListStart
  \myItem{Develop engaging content for social media platforms.}
  \myItem{Prepare reports and presentations summarizing research findings.}
\itemListEnd
}
\fi


% -------------------- AWARDS & HONORS --------------------
\sectionBlock{
\section{Awards\\and\\Honors}
}{
\awardListStart
\justifying
\item \emph{Provincial Third Prize}, Engineering Practice Competition (2025). \hfill 2025.03
Core Team Member Developed a vision-guided robotic sorting system for household waste classification.
% \item \emph{Best Innovation Award}, Tech Startup Pitch Competition \hfill 2023.05
% \item \emph{Excellence in Research Award}, Annual Research Symposium, \hfill 2022.12
% \item \emph{Academic Scholarship}, Tsinghua University \hfill 2022.09
\awardListEnd
}

% -------------------- SKILLS --------------------
\sectionBlock{
\section{Skills}
}{
\skillListStart
\justifying
\item \emph{Languages}: Chinese, English.
\item \emph{Programming}: {\Courier \fontsize{11pt}{11pt}\selectfont Python},
                          {\Courier \fontsize{11pt}{11pt}\selectfont C/C++}, 
                          {\Courier \fontsize{11pt}{11pt}\selectfont R},
                          {\Courier \fontsize{11pt}{11pt}\selectfont MATLAB}.
\item \emph{Robotics \& Hardware}: PyTorch, STM32, Arduino, ESP32, PCB Design.
\item \emph{Simulation \& Tools}: SolidWorks, COMSOL Multiphysics, AutoCAD.
\item \emph{Web \& Others}: HTML/CSS, Git, Linux, Astro (Personal Blog).
\skillListEnd
}

\iffalse
% -------------------- OTHERS --------------------
\sectionBlock{
\section{Academic Services}
}{
\skillListStart
\justifying
\item \emph{Reviewers for}: \textit{Journal of Operations Research and Optimization},
\item \phantom{\emph{Reviewers for}:} \textit{International Conference on Optimization and Machine Learning},
\item \phantom{\emph{Reviewers for}:} \;...
\skillListEnd
}
\fi

\end{document}

